$Z_3$ topological order in the quantum dimer-pentamer model

### 2016-08-02 qdpm_paper.tex
pulling

The gauge symmetry allows one to construct a gauge invariant string operator $S_\gamma$ along an oriented path $\gamma$ path on the dual lattice. We first orient all the links of the square lattice such that they point from the $A$ sublattice to the $B$ sublattice (see \figref{fig:orientedSL}) and define an oriented dimer flux $\Phi_\gamma$ through the path:
\begin{equation}
\Phi_\gamma \equiv \sum_{\ell \in \gamma} \rm{sgn}\left(\ell,\gamma\right) n_\ell
\end{equation}
where $\mathrm{sgn}(\ell,\gamma)$ is positive (negative) if $\ell$ is oriented to the right with respect to the orientation of $\gamma$. Additionally, we define background flux $\tilde{\Phi}_\ell$
\begin{equation}
\tilde{\Phi}_\gamma \equiv - \sum_{\ell \in \gamma} \rm{sgn}\left(\ell,\gamma\right) \tilde{n}_\ell
\end{equation}
where $n_\ell$ is the number operator for a static background dimer configuration which is chosen to fix the gauge, and the total charge enclosed in a closed loop $\Gamma$ is $Q_\Gamma = \Phi_\Gamma+ \tilde{\Phi}_\Gamma$. (Alternately can think of the source of $\tilde{\Phi}_\Gamma$ to be static charges of charge $+c_0$ ($-c_0$) sitting at the verticies of the $A$($B$) sub-lattice.).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fixed dimer number constraints}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fixed dimer parity constraints}

We now consider relaxing the local constraint to a parity constraint such that only $Q_v^{Z_2} \equiv (Q_v \mod 2)$ is required to vanish; the resulting GQDM are the even and odd sectors are the  even \& odd Ising gauge theories (IGT) (and the closely related even and odd sector Toric Codes). In these cases, the local constraint requires $\alpha_v \in \{ 0, \pi\}$ in \Eqref{eq:Gv} and therefore the gauge symmetry is reduced from $U(1)$ to $Z_2$. The set of allowed dimer resonances $\mathcal{C}_{\rm{TC}}$ is expanded accordingly:
\begin{align}
\mathcal{C}_{\rm{TC}} &\equiv \bigl\{ \left(c_{\Box,i},\bar{c}_{\Box,i}\right) \bigr\} \\
&=\bigl\{
\left(\vrtplqt,\hrzplqt\right),\left(\threeleftplqt,\oneleftplqt\right),\left(\twodownplqt,\twoupplqt\right),\left(\bplqt,\fplqt\right) \bigr\}
\end{align}
where we implicitly include rotational symmetry related resonances. We will limit or discussion to $v_\bplqt=0$ such that the corresponding Hamiltonian is
\begin{equation}
\HIGT\left(t\right) \equiv \HGQDM \biggl( \mathcal{C}_{\rm{IGT}},\bigl\{ \left(t,0\right) \bigr\} \biggr).
\end{equation}
In this case the equal superposition RK wavefunction is the exact ground state occurs in the absence of a potential energy term, as we can define a projection operator on each plaquette
\begin{equation}
h_\Box \equiv \frac{1}{2} \left( \mathbb{1} - \sum_i \eket{c_{\Box,i}}\ebra{\bar{c}_{\Box,i}} + h.c. \right)
\end{equation}
such that $\HIGT$ takes the form of \Eqref{eq:HRK} (up to a constant), and the RK state is the ground state for all values of $t$.

@@

The Hamiltonian of the QDPM is defined by \Eqref{eq:HGQDM} including both plaquette flips as well as local dimer resonances that create and destroy pairs of pentamers, and allow single pentamers to translate on the same sub-lattice (see \tabref{tab:pentamer_moves}). Thus we may write $\HQDPM$ as the following:
\begin{equation}
\HQDPM \equiv \HQDM + H_{\rm{pent}}
\end{equation}
where $H_{\rm{pent}}$ only involves the resonances in \tabref{tab:pentamer_moves} involving pentamers.

\begin{table}
    \begin{tabular}{| l | c | c |}
  	\hline
     & $c$ & $\bar{c}$ \\
	\hline
    $i$ & $\pentmvcreate$ &  $\pentmvanal$  \\
	\hline
    $ii$ &$\penmvhrzleft$&$\penmvhrzright$ \\
	\hline
    $iii$ &$\penmvdiagup$& $\penmvdiagdown$\\
	\hline
  \end{tabular}
  \caption{The pairs of local dimer \& pentamer configurations $c\leftrightarrow\bar{c}$ generate minimal local dynamics that create/annihilate pairs ($i$) of pentamers and translate single pentamers ($ii$ \& $iii$). Note that pentamers always stay on the same sublattice which is associated with their $U(1)$ charge. }
  \label{tab:pentamer_moves}
\end{table}

@@

Our numerical simulations (discussed below in \secref{sec:numerics}) suggest that the dynamics of $\HQDPM$ are ergodic in each topological sector. The exact zero energy ground state at the RK point, where $t_i=v_i, i \in \{ 0,1,2,3\}$, is the RK state, where the superposition is taken to be over all states in the topological sector $\Omega$ which are labeled by the topological loop operators
\begin{equation}
\Omega = \left(W_X^{\rm{QDPM}},W_Y^{\rm{QDPM}} \right)
\end{equation}
Since the $W_{X,Y}^{\rm{QDPM}}$ operators have eigenvalues $\{0,1,-1\}$...

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Study of the RK ground state of the QDPM}
\label{sec:numerics}

To determine the nature of the ground state at the RK point of the QDPM, we have used Monte Carlo sampling of $\ket{\Psi_{\rm{RK}}}$, using local updates corresponding to the dimer resonances shown in \tabref{tab:pentamer_moves} to compute ground state expectation values. Below we present the results of calculations on $L\times L$ lattices with periodic boundary conditions on systems up to $L=64$.

@@

We explicitly demonstrate how the extensive topological degeneracy of the QDM is reduced to a finite degeneracy in the QDPM by computing the histogram of $U(1)$ topological winding number $\Phi_X$ . This is shown in \figref{fig:u1_wind_qdpm}, where the different colors represent calculations that were initialized to different winding sectors; we confirm that $\Phi_{X/Y}$ is only conserved modulo $3$, rather than strictly conserved as it is in the QDM. We find that $P(\Phi_{X/Y})$ has a roughly gaussian envelope with a width that scales with system size--this is expected as $\Phi_{X/Y} = \pm L/2$ correspond to ordered configurations and thus there are fewer dimer configurations near these limits. Thus we find that the QDPM has a \emph{finite} $9$-fold degeneracy on the torus, where the topological sectors are labeled by $\Phi_{X/Y} \mod 3$, or equivalently $(W_X^{\rm{QDPM}},W_Y^{\rm{QDPM}})$, in contrast with the extensive degeneracy of the QDM. Additionally, we find no evidence of a lack of ergodicity within each of the 9 topological sectors. For the remainder of the paper we present results in the $(0,0)$, topological sector, but we see no dependence the topological sector for any of the results presented here~\note{Owen: which calculations/system sizes have you checked different topological sectors?}.
%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[]
    \centering
    \includegraphics[width=1.0\linewidth]{u1_wind_qdpm.pdf}
    \caption{The histogram of the $U(1)$ winding number $\Phi_X$ as measured in the QDPM on a
    $L=32$ lattice. Different colors correspond to calculations initialized to different winding sectors. Note that $\Phi_X$ is conserved modulo $3$, resulting in a $9$-fold topological degeneracy on a torus.
    \note{Owen: change the y-axis label to $P(\Phi_x)$ and the x-axis to $\Phi_x$. Is this still an $L=32$ lattice? Do you have $L=64$? Perhaps put both on the same plot? (with no vertical bars)}}
    \label{fig:u1_wind_qdpm}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

Here we discuss the dimer density correlations in the RK ground state of the QDPM. In \figref{fig:dimer_gry_scale_qdpm} we plot the bare dimer-dimer correlation function $\langle n_{\bm{0}} n_{\bm{r}}\rangle$ on an $L=16$ lattice; here the origin $\bm{0}$ represents the blue link, and $\bm{r}$ varies over all other links of the lattice. We see no evidence of symmetry breaking in the dimer correlations on lattices up $L=64$. We will restrict the rest of our disucssion to correlations between horizontal of dimers, as we find no rotational symmetry breaking, or qualitative difference between the the correlations between parallel dimers and perpendicular dimers.

%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}
        \centering
        \includegraphics[width=1.0\columnwidth]{dimer_gry_scale_qdpm.pdf}
        \caption{({\it left}) Gray scale of the dimer-dimer correlation function $\langle n_0 n_{\bm{r}}\rangle$ on an $L=16$ lattice. The origin corresponds to the blue link, and $\bm{r}$ varies over all other links of the lattice. Red links have correlations that are off the given scale.~\note{Owen: Is this the bare or connected correlation function? What do these plots look like on a log scale?} ({\it right}) $Z_3$ magnetic string correlation function. }
        \label{fig:dimer_gry_scale_qdpm}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

The left panel of \figref{fig:structure_factor} shows the equal-time dimer-dimer structure factor, 
\begin{equation}
S\left( \bm{q} \right) \equiv \frac{1}{ L^2} \sum_{i,j} e^{-i \bm{q} \cdot \left(\bm{r}_i - \bm{r}_j\right)} \left \langle n_i n_j \right \rangle
\end{equation}
where we restrict the sum to horizontal links.

%%%%%%%%%%%%%%%%%%%%%%%
   \begin{figure}[]
        \centering
        \includegraphics[width=1.0\columnwidth]{qdpm_dmr_vis_HM_16x16.pdf}
        \caption{QDPM dimer structure factor $\gamma=0.5$.}
        \label{fig:structure_factor}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}[]
        \centering
        \includegraphics[width=1.0\columnwidth]{vis_dmr_qdpm_struc_fac_32x32.pdf}
        \caption{The QDPM dimer structure factor $S_d(k)$ and $Z_3$ vison structure factor $S_v(k)$
        shown along the path in $k$ space connecting the $(0,0)$, to $(\pi,0)$, $(\pi,\pi)$, $(0,0)$
        points for $\gamma=0.5$.}
        \label{fig:vis_dmr_cut}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[width=1.0\columnwidth]{spatial_cors_parallel.pdf}
    \caption{Correlation function between parallel dimers on the same (blue) and different (red) 
    sub-lattice for a $L=64$ lattice. \note{Owen: Which direction is this? Do you have data for the perpendicular direction?}}
    \label{fig:spatial_dmr_cor}
\end{figure}
%    The lines represent least-squares fits to exponential decay. }
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[width=1.0\columnwidth]{spatial_cors_perp.pdf}
    \caption{Correlation function between perpendicular dimers on the same (blue) and different (red) 
    sub-lattice for a $L=64$ lattice.}
    \label{fig:spatial_dmr_cor}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[width=1.0\columnwidth]{spatial_cors_z3_vis.pdf}
    \caption{ $Z_3$ vison correlation function for $L=64$ lattice.}
    \label{fig:spatial_dmr_cor}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%

    \begin{figure}[]
        \centering
        \includegraphics[width=1.0\columnwidth]{monomer_cor_log.pdf}
        \caption{Monomer correlations in the QDPM.}
        \label{fig:vis_dmr_cut}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%

>>>>

The gauge symmetry allows one to construct a gauge invariant string operator $S_\gamma$ along an oriented path $\gamma$ path on the dual lattice. We first orient all the links of the square lattice such that they point from the $A$ sublattice to the $B$ sublattice (see \figref{fig:orientedSL}) and define an oriented dimer flux $\Phi_\gamma$ through the path:
\begin{equation}
\Phi_\gamma \equiv \sum_{\ell \in \gamma} \rm{sgn}\left(\ell,\gamma\right) n_\ell
\end{equation}
where $\mathrm{sgn}(\ell,\gamma)$ is positive (negative) if $\ell$ is oriented to the right with respect to the orientation of $\gamma$. Additionally, we define background flux $\tilde{\Phi}_\ell$
\begin{equation}
\tilde{\Phi}_\gamma \equiv - \sum_{\ell \in \gamma} \rm{sgn}\left(\ell,\gamma\right) \tilde{n}_\ell
\end{equation}
where $n_\ell$ is the number operator for a static background dimer configuration which is chosen to fix the gauge, and the total charge enclosed in a closed loop $\Gamma$ is $Q_\Gamma = \Phi_\Gamma+ \tilde{\Phi}_\Gamma$. (Alternately can think of the source of $\Phi_\Gamma$ to be static charges of charge $+c_0$ ($-c_0$) sitting at the verticies of the $A$($B$) sub-lattice.).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fixed number constraints}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fixed parity constraints}

We now consider relaxing the local constraint to a parity constraint such that only $Q_v^{Z_2} \equiv (Q_v \mod 2)$ is required to vanish; the resulting GQDM are the even and odd sectors are the  even \& odd Ising gauge theories (IGT) (and the closely related even and odd sector Toric Codes). In these cases, the local constraint requires $\alpha_v \in \{ 0, \pi\}$ in \Eqref{eq:Gv} and therefore the gauge symmetry is reduced from $U(1)$ to $Z_2$. The set of allowed dimer resonances $\mathcal{C}_{\rm{TC}}$ is expanded accordingly \textcolor{red}{Owen: Add symbols for 4-0 resonance, and 1-3 resonances and 2-2 resonance}:
\begin{align}
\mathcal{C}_{\rm{TC}} &\equiv \bigl\{ \left(c_{\Box,i},\bar{c}_{\Box,i}\right) \bigr\} \\
&=\bigl\{
\left(\vrtplqt,\hrzplqt\right),\left(\threeleftplqt,\oneleftplqt\right),\left(\twodownplqt,\twoupplqt\right),\left(\bplqt,\fplqt\right) \bigr\}
\end{align}
where we implicitly include rotational symmetry related resonances. We will limit or discussion to $v_\bplqt=0$ such that the corresponding Hamiltonian is
\begin{equation}
\HIGT\left(t\right) \equiv \HGQDM \biggl( \mathcal{C}_{\rm{IGT}},\bigl\{ \left(t,0\right) \bigr\} \biggr).
\end{equation}
In this case the equal superposition RK wavefunction is the exact ground state occurs in the absence of a potential energy term, as we can define a projection operator on each plaquette
\begin{equation}
h_\Box \equiv \frac{1}{2} \left( \mathbb{1} - \sum_i \eket{c_{\Box,i}}\ebra{\bar{c}_{\Box,i}} + h.c. \right)
\end{equation}
such that $\HIGT$ takes the form of \Eqref{eq:HRK} (up to a constant), and the RK state is the ground state for all values of $t$.

@@

The Hamiltonian of the QDPM is defined by \Eqref{eq:HGQDM} including both plaquette flips as well as local dimer resonances that create and destroy pairs of pentamers, and allow single pentamers to translate on the same sub-lattice (see \figref{fig:pentamer_moves}). Thus we may write $\HQDPM$ as the following:
\begin{equation}
\HQDPM \equiv \HQDM + H_{\rm{pent}}
\end{equation}
where $H_{\rm{pent}}$ only involves the resonances in \figref{fig:pentamter_moves} involving pentamers.

\begin{table}
    \begin{tabular}{| l | c | c |}
  	\hline
     & $c$ & $\bar{c}$ \\
	\hline
    $i$ & $\pentmvcreate$ &  $\pentmvanal$  \\
	\hline
    $ii$ &$\penmvhrzleft$&$\penmvhrzright$ \\
	\hline
    $iii$ &$\penmvdiagup$& $\penmvdiagdown$\\
	\hline
  \end{tabular}
  \caption{The pairs of local dimer \& pentamer configurations $c\leftrightarrow\bar{c}$ generate minimal local dynamics that create/annihilate pairs ($i$) of pentamers and translate single pentamers ($ii$ \& $iii$). Note that pentamers always stay on the same sublattice which is associates with their $U(1)$ charge. }
  \label{tab:pentamerMoves}
\end{table}

@@

Our numerical simulations (discussed below in \ref{sec:???}) suggest that the dynamics of $\HQDPM$ are ergodic in each topological sector. The exact zero energy ground state at the RK point, where $t_i=v_i, i \in \{ 0,1,2,3\}$, is the RK state, where the superposition is taken to be over all states in the topological sector $\Omega$ which are labeled by the topological loop operators
\begin{equation}
\Omega = \left(W_X^{\rm{QDPM}},W_Y^{\rm{QDPM}} \right)
\end{equation}
Since the $W_{X,Y}^{\rm{QDPM}}$ operators have eigenvalues $\{0,1,-1\}$...

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Study of the RK ground state of the QDPM}

To determine the nature of the ground state at the RK point of the QDPM, we have used Monte Carlo sampling of $\ket{\Psi_{\rm{RK}}}$, using local updates corresponding to the dimer resonances shown in \tabref{tab:pentamerMoves} to compute ground state expectation values. We studied $L\times L$ lattices with periodic boundary conditions on systems up to $L=64$.

@@

We explicitly demonstrate how the extensive topological degeneracy of the QDM is reduced to a finite degeneracy in the QDPM by computing the histogram of $U(1)$ topological winding number $\Phi_X$ . This is shown in \figref{fig:u1_wind_qdpm}, where the different colors represent calculations that were initialized to different winding sectors; we confirm that $\Phi_{X/Y}$ is only conserved modulo $3$, rather than strictly conserved as it is in the QDM. We find that $P(\Phi_{X/Y})$ has a roughly gaussian envelope with a width that scales with system size--this is expected as $\Phi_{X/Y} = \pm L/2$ correspond to ordered configurations and thus there are fewer dimer configurations near these limits. Thus we find that the QDPM has a \emph{finite} $9$-fold degeneracy on the torus, where the topological sectors are labeled by $\Phi_{X/Y} \mod 3$, or equivalently $(W_X^{\rm{QDPM}},W_Y^{\rm{QDPM}})$, in contrast with the extensive degeneracy of the QDM. For the remainder of the paper we present results in the $(0,0)$, topological sector, but we see no dependence the topological sector for any of the results presented here~\note{Owen: which calculations/system sizes have you checked different topological sectors?}.
%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[]
    \centering
    \includegraphics[width=1.0\linewidth]{u1_wind_qdpm.pdf}
    \caption{The histogram of the $U(1)$ winding number $\Phi_X$ as measured in the QDPM on a
    $L=32$ lattice. Different colors correspond to calculations initialized to different winding sectors. Note that $\Phi_X$ is conserved modulo $3$, resulting in a $9$-fold topological degeneracy on a torus.
    \note{Owen: change the y-axis label to $P(\Phi_x)$ and the x-axis to $\Phi_x$. Is this still an $L=32$ lattice? Do you have $L=64$? Perhaps put both on the same plot? (with no vertical bars)}}
    \label{fig:u1_wind_qdpm}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

Here we discuss the dimer density correlations in the RK ground state of the QDPM. In \figref{fig:dimer_gry_scale_qdpm} we plot the bare dimer-dimer correlation function $\langle n_{\bm{0}} n_{\bm{r}}\rangle$ on an $L=16$ lattice; here the origin $\bm{0}$ represents the blue link, and $\bm{r}$ varies over all other links of the lattice. We see no evidence of symmetry breaking in the dimer correlations on lattices up $L=64$.

@@

%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}
        \centering
        \includegraphics[width=1.0\columnwidth]{dimer_gry_scale_qdpm.pdf}
        \caption{({\it left}) Gray scale of the dimer-dimer correlation function $\langle n_0 n_{\bm{r}}\rangle$ on an $L=16$ lattice. The origin corresponds to the blue link, and $\bm{r}$ varies over all other links of the lattice. Red links have correlations that are off the given scale.~\note{Owen: Is this the bare or connected correlation function? What do these plots look like on a log scale?} ({\it right}) $Z_3$ magnetic string correlation function. }
        \label{fig:dimer_gry_scale_qdpm}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[width=1.0\columnwidth]{spacial_cors_parallel.pdf}
    \caption{Correlation function between parallel dimers on the same (blue) and different (red) 
    sub-lattice for a $L=64$ lattice. \note{Owen: Which direction is this? Do you have data for the perpendicular direction?}}
    \label{fig:spatial_dmr_cor}
\end{figure}
%    The lines represent least-squares fits to exponential decay. }
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[width=1.0\columnwidth]{spacial_cors_perp.pdf}
    \caption{Correlation function between perpendicular dimers on the same (blue) and different (red) 
    sub-lattice for a $L=64$ lattice.}
    \label{fig:spatial_dmr_cor}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[width=1.0\columnwidth]{spacial_cors_z3_vis.pdf}
    \caption{ $Z_3$ vison correlation function for $L=64$ lattice.}
    \label{fig:spatial_dmr_cor}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%

   \begin{figure}[]
        \centering
        \includegraphics[width=1.0\columnwidth]{qdpm_dmr_vis_HM_16x16.pdf}
        \caption{QDPM dimer structure factor $\gamma=0.5$.}
        \label{fig:spacial_dmr_z3vis_cor}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}[]
        \centering
        \includegraphics[width=1.0\columnwidth]{vis_dmr_qdpm_struc_fac_32x32.pdf}
        \caption{The QDPM dimer structure factor $S_d(k)$ and $Z_3$ vison structure factor $S_v(k)$
        shown along the path in $k$ space connecting the $(0,0)$, to $(\pi,0)$, $(\pi,\pi)$, $(0,0)$
        points for $\gamma=0.5$.}
        \label{fig:vis_dmr_cut}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Monomer correlations}

%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}[]
        \centering
        \includegraphics[width=1.0\columnwidth]{monomer_cor_log.pdf}
        \caption{Monomer correlations in the QDPM.}
        \label{fig:vis_dmr_cut}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
    \begin{tabular}{| l | c | c |}
  	\hline
     & $c$ & $\bar{c}$ \\
	\hline
    $i$ & $\monomermvA$ &  $\monomermvB$  \\
    \hline
  \end{tabular}
  \caption{The pair of local dimer \& monomer configurations $c\leftrightarrow\bar{c}$ generate
  minimal local monomer dynamics. Monomers always remain on their origonal sublattice. }
  \label{tab:pentamerMoves}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
